---
title: "Module 9 - Developing Data Products / Coursera Data Science Specialisation"
author: "P. Physics"
date: "29 January 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressMessages(library(leaflet))
```

## Using Leaflet to produce an interactive map

The map below locates a completely biased choice of key institutions in Geneva, the European Center for Nuclear Research (CERN), the University of Geneva (UNIGE), the United Nation (UNOG) and the World Economic Forum. If you want to know more about these unique places in Geneva, please visit the websites' links embedded in each icon.

```{r cars, echo=FALSE}
coordinates <- data.frame(
  lat = c(46.2,46.233058,46.235531,46.222665776),
  long = c(6.1667,6.055692,6.204483,6.137666116)
)
websites <- c(
  "<a href='http://www.unige.ch/sciences/index.html'>University of Geneva </a>",
  "<a href='http://home.cern/'>The CERN Website </a>",
  "<a href='https://www.weforum.org/'>World Economic Forum </a>",
  "<a href='http://www.unog.ch/'>United Nations </a>"
)

coordinates %>% leaflet() %>% addTiles() %>% addMarkers(popup=websites)
# same notation as my_map = addMarkers(my_map, ...)
#coordinates
```

